---
title: "Case-selection strategies walkthrough"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Case-selection strategies walkthrough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(caseselectR)

data(toy_cross, package = "caseselectR")
typ <- typical_case(toy_cross, Y ~ X | Z1 + Z2)
dev <- deviant_cases(toy_cross, Y ~ X | Z1 + Z2, n = 2)
typ; head(dev$results)

### vignettes/panel.Rmd
```r
---
title: "Panel workflows (longitudinal, index)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Panel workflows (longitudinal, index)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(caseselectR)
data(toy_panel, package = "caseselectR")
long <- longitudinal_cases(toy_panel, Y ~ X | Z1, id = unit, time = t, n = 2)
idx  <- index_cases(toy_panel, Y ~ X | Z1, id = unit, time = t)
long; idx

### vignettes/transparency.Rmd
```r
---
title: "Transparency & audit logs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Transparency & audit logs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(caseselectR)
data(toy_cross, package = "caseselectR")
res <- typical_case(toy_cross, Y ~ X | Z1 + Z2, seed = 123)
res$audit_log   # Reproducible 7-step audit trail
